---
title: "R for Data Science - Chapter 3: Data visualisation "
output: html_notebook
---

# **Chapter 3: Data Visualisation**

#### 1. Do cars with big engines use more fuel than cars with small engines? 
#### 2. What does the relationship between engine size and fuel efficiency look like?
#### 3. Is it positive? Negative? Linear? Nonlinear?
```{r 3.2 First steps}
ggplot(data=mpg) + 
  geom_point(mapping = aes(x=displ, y=hwy))
```


```{r}
#graph template
#ggplot(data = <DATA>) + 
#  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
?mpg
```
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x=cyl, y=hwy))
```
```{r 3.3 Aesthetic}
#?geom_point
ggplot(data = mpg) + 
  geom_point(mapping = aes(x=displ, y=hwy, color=class))
```
#### **Facets are special for CATEGORICAL VARIABLES**
```{r 3.5 Facets}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color='red') + 
  facet_grid(drv ~ cyl)
```
```{r 3.6 Geometric objects}
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy))
              
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy, group = drv))
    
ggplot(data = mpg) +
  geom_smooth(
    mapping = aes(x = displ, y = hwy, color = drv),
    show.legend = FALSE
  )
```
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(x = displ, y = hwy))
```
#### **Making global mappings without changing every x~y values**
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = class)) + 
  geom_smooth()
```
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = class)) + 
  geom_smooth(data = filter(mpg, class == "subcompact"), se = FALSE)
```
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = F)
```
```{r 3.6.1 Excersices}
ggplot(data=mpg, mapping=aes(x=displ, y=hwy)) +
  geom_point() +
  geom_smooth(se=F)

ggplot(data=mpg, mapping=aes(x=displ, y=hwy, group=drv)) +
  geom_point() +
  geom_smooth(se=F)
```
```{r}
ggplot(data=mpg, mapping=aes(x=displ, y=hwy, color=drv)) +
  geom_point() +
  geom_smooth(se=F)

ggplot(data=mpg, mapping=aes(x=displ, y=hwy)) +
  geom_point(mapping=aes(color=drv)) +
  geom_smooth(se=F)
```
```{r}
ggplot(data=mpg, mapping=aes(x=displ, y=hwy)) +
  geom_point(mapping=aes(color=drv)) +
  geom_smooth(mapping=aes(linetype=drv), se=F)

ggplot(data=mpg, mapping=aes(x=displ, y=hwy, color=drv)) +
  geom_point(shape=21, fill='white', size=5, stroke=5)
```
## **3.7 Statistical transformations**
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut))
```
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, colour = cut))

ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = cut))
```
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = clarity))
```
```{r}
ggplot(data = diamonds, mapping = aes(x = cut, fill = clarity)) + 
  geom_bar(alpha = 1/5, position = "identity")

ggplot(data = diamonds, mapping = aes(x = cut, colour = clarity)) + 
  geom_bar(fill = NA, position = "identity")
```
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = clarity), position = "fill")
```
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = clarity), position = "dodge")
```
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), position = "jitter")
```


```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_jitter() 

ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_count()
```


```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color=drv)) + 
  geom_boxplot(position = 'dodge2')
```

### **3.9 Coordinate systems**
```{r}
ggplot(data = mpg, mapping = aes(x = class, y = hwy)) + 
  geom_boxplot()

ggplot(data = mpg, mapping = aes(x = class, y = hwy)) + 
  geom_boxplot() +
  coord_flip()
```


```{r}
nz <- map_data("nz")

ggplot(nz, aes(long, lat, group = group)) +
  geom_polygon(fill = "white", colour = "black")

ggplot(nz, aes(long, lat, group = group)) +
  geom_polygon(fill = "white", colour = "black") +
  coord_quickmap()
```


```{r}
bar <- ggplot(data = diamonds) + 
  geom_bar(
    mapping = aes(x = cut, fill = cut), 
    show.legend = FALSE,
    width = 1
  ) + 
  theme(aspect.ratio = 1) +
  labs(x = NULL, y = NULL)

bar + coord_flip()
bar + coord_polar()
```
### **3.10 The layered grammar of graphics**
#### position adjustments, stats, coordinate systems, and faceting to our code template:
                ggplot(data = <DATA>) + 
                  <GEOM_FUNCTION>(
                     mapping = aes(<MAPPINGS>),
                     stat = <STAT>, 
                     position = <POSITION>
                  ) +
                  <COORDINATE_FUNCTION> +
                  <FACET_FUNCTION>